Modelling the emergence of whisker barrels

### 2020-06-13 paper/briefpaper/brief.tex
Last bit of Friday work
Updates the text for the section on modifying the noise applied to a_i at t=0

\cmnt{We performed a sensitivity analysis to determine if the quality of the
  pattern was affected by perturbations to any of the following inputs:
%
  i)~the magnitude and offset of the noise applied to $a_i$ at $t=0$;
%
  ii)~random noise applied to the interaction parameters, $\gamma_{i,j}$;
%
  iii)~random noise (of various length scales) applied to the guidance fields;
%
  and
%
  iv)~The angle and magnitude of one of the guidance fields, ($\rho_1$;
  Fig.\,\ref{fig:main}A).
%
  We analysed the effect on the three pattern metrics, $\delta$ (the Honda
  Voronoi metric), $\eta$ (the pattern-match metric) and $\omega$ (which
  measures localization of connections, $c_i$) evaluated after 30000
  simulation steps.}

\cmnt{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The results (where deviations occur as a
  result of the different random initial conditions for $a_i$) were
  $\delta=0.089\pm{0.004}$, $\eta=113.5\pm{1.2}$ and
  $\omega=0.2165\pm{0.0001}$. None of the three metrics were strongly affected
  by the random initial conditions for $a_i$. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\cmnt{Next, we changed the initial condition for $a_i$, changing the
  parameters of the generating uniform distribution to set each hex to
  $0.4+{U}(0,0.4)$. We ran this system 10 times and obtain the result
  $\delta=0.0\pm{0.000}$, $\eta=100\pm{0}$ and $\omega=0.2ish\pm{0.0000}$. A
  t-test demonstrates that this is ????. A final test of a noise-free initial
  condition with $a_i=0.2$ for every hex also ????.}

>>>>

\cmnt{We performed a sensitivity analysis to determine if the quality of the
  pattern was affected by perturbations to any of the following inputs:
%
  i)~the magnitude and offset of the noise applied to $a_i$ at $t=0$;
%
  ii)~random noise applied to the interaction parameters, $\gamma_{i,j}$;
%
  iii)~random noise (at various length scales) applied to the guidance fields;
%
  and
%
  iv)~The angle and magnitude of one of the guidance fields, ($\rho_1$;
  Fig.\,\ref{fig:main}A).
%
  In the following analysis, we always evaluated the three pattern metrics,
  $\delta$ (the Honda Voronoi metric), $\eta$ (the pattern-match metric) and
  $\omega$ (which measures localization of connections, $c_i$) after running
  the model for 30000 simulation steps.}

\cmnt{First, we conducted 10 runs of the simulation shown in
  Fig.\,\ref{fig:main}C to evaluate the mean and standard deviation of the
  three metrics in the default model. The
  results (where deviations occur as a result of the different random initial
  conditions for $a_i$) were $\delta=0.089\,(0.004)$, $\eta=113.5\,(1.2)$ and
  $\omega=0.2165\,(0.0001)$. None of the three metrics were strongly affected
  by the random changes to $a_i$ on each run. The results give a baseline from
  which to evaluate whether changes in the other inputs have a statistically
  significant effect.}

\cmnt{Next, we modified the parameters of the generating uniform distribution
  to initialize $a_i$ for each hex to $0.1+{U}(0,0.4)$ (increasing the variability of
  $a_i(\mb{x},t=0)$ without changing the mean initial activation). We ran this
  system 10 times and obtained the results $\delta=0.090\,(0.005)$,
  $\eta=115\,(1.9)$ and $\omega=0.2166\,(0.0003)$. Paired two-sample t-tests
  demonstrated that the increase in noise amplitude made no significant
  difference to the metric results ($\delta:
  \mathrm{t}=-0.69,\mathrm{p}=0.49$,
  $\eta: \mathrm{t}=-2.0,\mathrm{p}=0.06$,
  $\omega: \mathrm{t}=-1.7,\mathrm{p}=0.11$). 10 runs of a
  noise-free initial condition with $a_i=0.3$ for every hex showed that
  the model is deterministic (all runs produced the results $\delta=0.0928$,
  $\eta=114.31$ and $\omega=0.21649$) and that stochasticity in
  $a_i(\mb{x},t=0)$ is not required by this model, as all three results lay within
  one standard deviation of those for the runs in which $a_i$ was initialized stochastically.}

% Quick check that noise free result is within 1 SD for the noisier initial conditions
%         Noisefree    Normal noise    NF SD from Normal?   Noisy            NF SD from Noisy?
% delta   0.0928       0.089(0.004)    <1                   0.090 (0.005)    <1
% eta     114.31       113.5(1.2)      <1                   115 (1.9)        <1
% omega   0.21649      0.2165(0.0001)  <1                   0.2166 (0.0003)  <1
